Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
removing highlighted text i agreed with

\ab{Here, for the theories described in Sec.~\ref{sec:review_theories}, we
use QNM calculations from the literature and determine
the coefficients in the ParSpec, which we have summarized
in Table~\ref{tab:ref_theories_qnms}.}
%
We consider only the fundamental QNM $(\ell, m, n) = (2, 2, 0)$,
hence we omit the QNM subscript ``$(2,2,0)$'' for brevity and, likewise,
the subscript ``f'' for final BH's spin and mass.

@@

For the nonrotating QNMs we use\sout{d} \abcomm{We are using present tense when
describing results in the paper, so I would suggest with stick with that consistently
in the Appendix.} the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
generate a new quartic fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
values of the coupling constant (see, in particular, Eq.~(27) and Fig.~2 of
Ref.~\cite{Blazquez-Salcedo:2016enn}).
%
We find,
%
\begin{subequations}
\begin{align}
    M {\rm Re}(\sigma)_{\rm EdGB} &= M {\rm Re}(\sigma)_{\rm GR} \, \left( 1 + 0.0107 \, \gamma_{\rm EdGB} \right),
    \\
    M {\rm Im}(\sigma)_{\rm EdGB} &= M {\rm Im}(\sigma)_{\rm GR} \, \left( 1 - 0.0044 \, \gamma_{\rm EdGB} \right).
\end{align}
\end{subequations}
%
% <<<<<<< HEAD
The small values of the numerical prefactors of $\gamma_{\rm EdGB}$ are a consequence of the how weakly the QNMs
% =======
% The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ \abcomm{the term above
% is linear not quartic in $\gamma_{\rm EdGB}$. Do you mean $\ell_{\rm EdGB}^4$?}
% are a consequence of \sout{the} how weakly the QNMs
% >>>>>>> 72e1d3e2d4db50f80c67fc8bc13cab1708d40edb
of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $\gamma_{\rm EdGB} \approx 0.3$.

The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
which for consistency with our previous discussion, we truncate at quartic-order in $\gamma_{\rm EdGB}$ \abcomm{$\ell_{\rm EdCS}^4$?}.
%
The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ \ab{can be}
read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
and re-expand in small coupling and spin.
%
These steps yield \ab{for} $p_{\rm EdGB} = 4$,
%
\begin{align}
     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
\end{align}
%
for the $j=0$ coefficients and
%
\begin{equation}
    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
\end{equation}
%
for the $j=1$ coefficients.

@@

\ab{We show} in Fig.~\ref{fig:corner_plot_all} a corner plot \ab{for all the} intrinsic binary parameters from our parameter-estimation study of GW150914, using the \pSEOB{} waveform models for GR and dCS.
%
We see that \ab{the} median\ab{s} of the \ab{posterior distributions are} not affected substantially by the inclusion of the non-GR parameters. \ab{This is particularly important for the $\Mf$ and $\chi_{\rm f}$ parameters, since
the ParSpec framework assumes that the non-GR theory induces small deviations from GR.}
%
We \ab{obtain} qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
%
We also remark that the fact that the posterior on $\chi_{\rm f}$ has most support around $\approx 0.7$ justifies our use
of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.

>>>>

Here, for the theories described in Sec.~\ref{sec:review_theories}, we
use QNM calculations from the literature and determine
the coefficients in the ParSpec, which we have summarized
in Table~\ref{tab:ref_theories_qnms}.
%
We consider only the fundamental QNM $(\ell, m, n) = (2, 2, 0)$,
hence we omit the QNM subscript ``$(2,2,0)$'' for brevity and, likewise,
the subscript ``f'' for final BH's spin and mass.

@@

For the nonrotating QNMs we use
% HS: I agree.
% \abcomm{We are using present tense when
% describing results in the paper, so I would suggest with stick with that consistently
% in the Appendix.}
the numerical data of Ref.~\cite{Blazquez-Salcedo:2016enn} and
generate a new \hs{linear} fit in $\gamma_{\rm EdGB} = \ell_{\rm EdCS} / M$ using numerical QNM data valid for small
values of the $\gamma_{\rm EdGB}$ (see, in particular, Eq.~(27) and Fig.~1 of
Ref.~\cite{Blazquez-Salcedo:2016enn}).
%
We find,
%
\begin{subequations}
\begin{align}
    M {\rm Re}(\sigma)_{\rm EdGB} &= M {\rm Re}(\sigma)_{\rm GR} \, \left( 1 + 0.0107 \, \gamma_{\rm EdGB} \right),
    \\
    M {\rm Im}(\sigma)_{\rm EdGB} &= M {\rm Im}(\sigma)_{\rm GR} \, \left( 1 - 0.0044 \, \gamma_{\rm EdGB} \right).
\end{align}
\end{subequations}
%
% <<<<<<< HEAD
The small values of the numerical prefactors of $\gamma_{\rm EdGB}$ are a consequence of the how weakly the QNMs
% =======
% The small values of the numerical prefactors of $\gamma_{\rm EdGB}^4$ \abcomm{the term above
% is linear not quartic in $\gamma_{\rm EdGB}$. Do you mean $\ell_{\rm EdGB}^4$?}
% are a consequence of \sout{the} how weakly the QNMs
% >>>>>>> 72e1d3e2d4db50f80c67fc8bc13cab1708d40edb
of BHs in EdGB gravity deviate from their GR counterparts, even at moderate values $\gamma_{\rm EdGB} \approx 0.3$.

The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
which for consistency with our previous discussion, we truncate at \hs{leading-order in} $\gamma_{\rm EdGB}$
% \abcomm{$\ell_{\rm EdCS}^4$?}.
%
\hs{We can expand the resulting formula} in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
and re-expand in small coupling and spin.
%
These steps yield \ab{for} $p_{\rm EdGB} = 4$,
%
\begin{align}
     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
\end{align}
%
for the $j=0$ coefficients and
%
\begin{equation}
    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
\end{equation}
%
for the $j=1$ coefficients.

@@

% HS: I agree with all the changes below
We show in Fig.~\ref{fig:corner_plot_all} a corner plot for all the intrinsic
binary parameters from our parameter-estimation study of GW150914, using the
\pSEOB{} waveform models for GR and dCS.
%
We see that the medians of the posterior distributions are not affected substantially by the inclusion of the non-GR parameters.
%
This is particularly important for the $\Mf$ and $\chi_{\rm f}$ parameters, since
the ParSpec framework assumes that the non-GR theory induces small deviations from GR.
%
We obtain qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
%
We also remark that the fact that the posterior on $\chi_{\rm f}$ has most support around $\approx 0.7$ justifies our use
of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.
